Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-01-31 paper.tex
Minor changes to section 4

\begin{proposition}
  Suppose that $G$ satisfies $\ddag'_{D + 4\delta+2}$. Then there exists $L$
  such that for $n$ sufficiently large there is a map $i^n_{n+1}\from \Skel_1
  K_n \to \Skel_1 K_{n+1}$ satisfying the following conditions:
  \begin{enumerate}
    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_L\Skel_1 K_n$,
    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$,
      and
    \item for each $n$, the map $i^n_{n+1}$ is affine homotopic to a map that
      factors through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
  \end{enumerate}
\end{proposition}

\begin{proof}
  Let $n_0$ and $L$ be the numbers given by the condition $\ddag'_{D + 8\delta
  + 2}$ and let $n \geq n_0$.

@@

\begin{proposition}\label{prop:extendingaffinemaps2}
  \todo{Proposition about extending affine maps.}
\end{proposition}

@@

\begin{definition}
  We say that $G$ satisfies $\S_M$ if there exists $k$ such that for any $n$
  sufficiently large and any simplicial map $f\from \sd^M\boundary\Delta^2 \to
  K_n$ that is a simplicial approximation to a map that factors through
  $p^\infty_n \from \boundary G \to K_n$, $f$ admits an extension to $\Delta^2$
  that is affine on $\sd^k \Delta^2$.
\end{definition}

@@

@@

We begin the proof of \cref{thm:ddagimpliesLCd} by proving the following 
proposition.

\begin{proposition}\label{prop:ddag_implies_i}
  Let $d \geq -1$. Suppose that $G$ satisfies the conditions $\S^{d-1}$ and
  $\ddag^{d}$. Then there are constants $n_0$, $k$ and $\epsilon$ such that for
  each $n\geq n_0$ there is map $i^n_{n+1}\from\Skel_{d+1} K_n \to \Skel_{d+1}
  K_{n+1}$ such that the following conditions hold.
  \begin{enumerate}
    \item For any $x \in \Vertices(K_n)$, $\dist(x, i_{n+1}^n(x)) \leq
      \epsilon$.
    \item The map $i^n_{n+1}$ is affine on the subdivision $\sd^k\Skel_{d+1}
      K_n$ of $\Skel_{d+1}K_n$.
    \item The map $i^n_{n+1}\restricted{\Skel_d K_n}$ admits a factoring.
  \end{enumerate}
\end{proposition}

\begin{proof}
  The condition $\ddag^{-1}$ implies the infinitude of $G$, so
  \cref{lem:near_geod_rays} is applicable. For $x \in \Vertices{K_n}$ choose an
  infinite geodesic ray $\alpha_x$ such that $\alpha(0) = 1$ and
  $\dist(\alpha(n), x) \leq 4\delta$. Define $i^n_{n+1}(x) =
  \alpha_x(n+1)$. Then $i^n_{n+1}$ satisfies the first requirement with
  $\epsilon = 4\delta+2$ and satisfies the second requirement automatically.

  Furthermore, $\alpha_x(\infty) \in V_{n+1}(\alpha_x(n+1))$, so 
  $p^\infty_{n+1}(\alpha_x(\infty))$ lies in a simplex of $K_{n+1}$ that also 
  contains $\alpha_x(n+1)$.  Therefore the map $i^n_{n+1}$ and a simplicial 
  approximation to the map $x \mapsto \alpha_x(\infty) \mapsto p^\infty_{n+1} 
  (\alpha_x(\infty))$ are related by an affine homotopy, so $i^n_{n+1}$ admits a 
  factoring.

  Now apply \cref{prop:extendingaffinemaps2} to extend $i^n_{n+1}$ from
  $\Vertices(K_n)$ to $\Skel_{d+1} K_n$ to obtain a map with the required
  properties.
\end{proof}

Throughout the remainder of this section we assume that $G$ satisfies $\ddag^{d-1}$ 
and $\S^{d}$. Let $n_0$, $k$ and $\epsilon$ be the constants given in 
\cref{prop:ddag_implies_i}, and for $n\geq n_0$ let $i^n_{n+1} 
\from \sd^k\Skel_{d+1} K_n \to \Skel_{d+1} K_{n+1}$ be the affine map given by 
that proposition.  For $n \geq m \geq n_0$ let $i^m_n$ be the composition 
$i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_{d+1} K_m \to 
\Skel_{d+1} K_n$.  This map is affine on a degree $k^{n-m}$ subdivision of 
$\Skel_{d+1} K_m$.

@@

\begin{lemma}\label{lem:useful}
  Let $(x_n)$ be a sequence of points in $G$ with $\dist(x_{n+1}, e) = 
  \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then,
  \begin{equation*}
    \gromov{e}{x_m}{x_n} \geq \dist(e,x_m) - C
  \end{equation*}
  for some constant $C$ depending only on $\delta$ and the bound on 
  $\dist(x_{n+1}, x_n)$.
\end{lemma}

@@

  By the triangle inequality it follows that for $n\geq m$ we have the following 
  inequality.
  \begin{equation*}
    \vdistance(\alpha_n(\infty), \alpha_m(\infty)) \leq C_1 a^{-i_m}
  \end{equation*}
  for some constants $C_1$ depending only on $\delta$ and $C_0$. Then, by
  definition of the visual metric, there exists a constant $C_2$ such that
  \begin{equation*}
    \gromov{e}{\alpha_n(\infty)}{\alpha_m(\infty)} \geq i_m - C_2.
  \end{equation*}

  Now, by \cref{lem:boundary_gromov_product} there exists a constant $C_3$ such
  that
  \begin{equation*}
    \gromov{e}{\alpha_n(i_n)}{\alpha_m(i_m)} \geq i_m - C_3,
  \end{equation*}
  as required.
\end{proof}

@@

  We now bound the distance $\dist(y_n, y_{n+1}$. To start with, $\dist(y_n,
  i^n_{n+1} y_n) \leq \epsilon$. Let $R$ be such that any two vertices in the
  1-skeleton of $\sd^k \Delta^{d+1}$ are joined by a path traversing at most
  $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$ containing
  $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$ and $y_{n+1}$ is a vertex of
  the image of $\sigma$ under $i^n_{n+1}$, so $\dist(i^n_{n+1} y_n, y_{n+1})
  \leq RD$.  Putting this together,
  \begin{equation*}
      \dist(y_n, y_{n+1}) \leq \epsilon + RD
  \end{equation*}

  It follows from \cref{lem:useful} that there exists a constant $C$ depending
  only on $\delta$, $\epsilon$ and $k$ such that $\gromov{e}{y_n}{y_m} \geq m -
  C$.

@@

\begin{proof}
  To start with, apply \cref{prop:extendingaffinemaps2} with $k = C + D$ to
  obtain constants $k'$ and $m_0\geq n_0$ such that the conclusion of the
  proposition holds.

  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta^{d+1}$ such
  that $f_0$ and $f_1$ are both affine on $J$. Then the map 
  \begin{equation*}
    f_0 \disjointunion f_1 \from J \times \{0\} \disjointunion J \times \{1\}
          \to K_n,
  \end{equation*}
  defined on a subset of the product simplicial complex $J \times [0,1]$,
  satisfies the conditions of \cref{prop:extendingaffinemaps2}, and so admits
  an affine extension $F \from \sd^{k'} (J \times [0,1]) \to K_n$. Let $h =
  i^n_\infty \composed F$, so $h$ is a homotopy from $i^n_\infty\composed f_0$
  to $i^n_\infty\composed f_1$ and it remains to prove the uniform continuity
  assertion.

@@

  Furthermore, $\dist(y, i^n_{n+1}(y))$ is uniformly bounded by the constant
  $\epsilon$ from \cref{prop:ddag_implies_i}, and $\newdist(i^n_{n+1}(y),
  i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by the product of $D$ and
  the constant $k$ appearing in \cref{prop:ddag_implies_i}. By putting all this
  together we obtain a bound $C$ on $\newdist(i^n_{n+1}\composed
  p^\infty_n(\xi), p^\infty_{n+1}(\xi))$, and then $\dist(x_1, x_2) \leq C +
  2D$.
\end{proof}

>>>>

\begin{proposition}\label{prop:i_in_dimension_1}
  Suppose that $G$ satisfies $\ddag'_{D + 4\delta+2}$. Then there exist $L$ and
  $n_0$ such that for $n\geq n_0$ there is a map $i^n_{n+1}\from \Skel_1 K_n
  \to \Skel_1 K_{n+1}$ satisfying the following conditions:
  \begin{enumerate}
    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_L\Skel_1 K_n$,
    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$,
      and
    \item for each $n$, the map $i^n_{n+1}$ is affine homotopic to a map that
      factors through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
  \end{enumerate}
\end{proposition}

\begin{proof}
  Let $n_0$ and $L$ be the numbers given by the condition $\ddag'_{D + 4\delta
  + 2}$ and let $n \geq n_0$.

@@

@@

\begin{definition}
  Let $\Delta$ be the standard 2-simplex.  We say that $G$ satisfies $\S_M$ if
  there exist $L$ and $n_0$ such that for any $n\geq n_0$ and any simplicial
  map $f\from \sd^M\boundary\Delta \to K_n$ that is a simplicial approximation
  to a map that factors through $p^\infty_n \from \boundary G \to K_n$, $f$
  admits an extension to $\Delta$ that is affine on $\sd^L \Delta$.
\end{definition}

@@

Thrououghout the rest of this section we assume that $G$ satisfies
\todo{conditions.}

@@

We begin the proof of \cref{thm:ddagimpliesLCd} by proving the following 
proposition, which extends the maps constructed in
Proposition~\ref{prop:i_in_dimension_1}.

\begin{proposition}\label{prop:i_in_dimension_2}
  There are constants $n_0$ and $L$ such that for each $n\geq n_0$ there is map
  $i^n_{n+1}\from\Skel_{d+1} K_n \to \Skel_{d+1} K_{n+1}$ such that the
  following conditions hold.
  \begin{enumerate}
    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_L\Skel_2 K_n$,
    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$,
      and
  \end{enumerate}
\end{proposition}

\begin{proof}
  \todo{Prove this}
\end{proof}

\begin{definition}
  With the notation of Proposition~\ref{prop:i_in_dimension_2}, for $n \geq m
  \geq n_0$ let $i^n_m \from \Skel_2 K_m \to \Skel_2 K_n$ be the composition
  $i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_{d+1} K_m \to 
  \Skel_{d+1} K_n$.  This map is affine on a degree $L^{n-m}$ subdivision of 
  $\Skel_{d+1} K_m$.
\end{definition}

@@

\begin{lemma}\label{lem:useful}
  \todo{Or quasi-geodesics?}
  Let $(x_n)$ be a sequence of points in $G$ with $\dist(x_{n+1}, e) = 
  \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then,
  \begin{equation*}
    \gromov{e}{x_m}{x_n} \geq \dist(e,x_m) - C
  \end{equation*}
  for some constant $C$ depending only on $\delta$ and the bound on 
  $\dist(x_{n+1}, x_n)$.
\end{lemma}

@@

  By the triangle inequality it follows that for $n\geq m$ we have the following 
  inequality.
  \begin{equation*}
    \vdistance(\alpha_n(\infty), \alpha_m(\infty)) \leq C_1 a^{-i_m}
  \end{equation*}
  for some constants $C_1$ depending only on $\delta$ and $C_0$. Then, by
  definition of the visual metric, there exists a constant $C_2$ such that
  \begin{equation*}
    \gromov{e}{\alpha_n(\infty)}{\alpha_m(\infty)} \geq i_m - C_2.
  \end{equation*}
  Now, by \cref{lem:boundary_gromov_product} there exists a constant $C_3$ such
  that
  \begin{equation*}
    \gromov{e}{\alpha_n(i_n)}{\alpha_m(i_m)} \geq i_m - C_3,
  \end{equation*}
  as required.
\end{proof}

@@

  We now bound the distance $\dist(y_n, y_{n+1})$. To start with, $\dist(y_n,
  i^n_{n+1} y_n) \leq 2\delta+1$. Let $R$ be $3\cdot 2^{k-1}$, so that any two
  vertices in the 1-skeleton of $\sd^k \Delta^{d+1}$ are joined by a path
  traversing at most $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$
  containing $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$ and $y_{n+1}$ is a
  vertex of the image of $\sigma$ under $i^n_{n+1}$, so $\dist(i^n_{n+1} y_n,
  y_{n+1}) \leq RD$.  Putting this together,
  \begin{equation*}
      \dist(y_n, y_{n+1}) \leq 2\delta + 1 + RD
  \end{equation*}

  It follows from \cref{lem:useful} that there exists a constant $C$ depending
  only on $\delta$ and $k$ such that $\gromov{e}{y_n}{y_m} \geq m -
  C$.

@@

\begin{proof}
  To start with, apply Proposition \todo{extending affine maps} with $k = C +
  D$ to obtain constants $k'$ and $m_0\geq n_0$ such that the conclusion of the
  proposition holds.

  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta^{d+1}$ such
  that $f_0$ and $f_1$ are both affine on $J$. Then the map 
  \begin{equation*}
    f_0 \disjointunion f_1 \from J \times \{0\} \disjointunion J \times \{1\}
          \to K_n,
  \end{equation*}
  defined on a subset of the product simplicial complex $J \times [0,1]$,
  satisfies the conditions of Proposition~\todo{extending maps}, and so admits
  an affine extension $F \from \sd^{k'} (J \times [0,1]) \to K_n$. Let $h =
  i^n_\infty \composed F$, so $h$ is a homotopy from $i^n_\infty\composed f_0$
  to $i^n_\infty\composed f_1$ and it remains to prove the uniform continuity
  assertion.

@@

  Furthermore, $\dist(y, i^n_{n+1}(y))$ is bounded by $2\delta+1$, and
  $\newdist(i^n_{n+1}(y), i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by
  the product of $D$ and the constant $k$ appearing in
  \cref{prop:i_in_dimension_2}. By putting all this together we obtain a bound
  $C$ on $\newdist(i^n_{n+1}\composed p^\infty_n(\xi), p^\infty_{n+1}(\xi))$,
  and then $\dist(x_1, x_2) \leq C + 2D$.
\end{proof}
